---
title: "battleship"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{battleship}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Battleship is a guessing game where two players have a fleet of ships on two boards. The players' boards are hidden from each other so that one cannot see where the other's fleet are positioned.

The board is usually a 10x10 grid like so:

![](https://upload.wikimedia.org/wikipedia/commons/6/65/Battleship_game_board.svg)

Here the gray rectangles represent the ships on the board.

Taking alternate turns, each player then guesses a square. The other player then tells them whether the guess was correct or incorrect. The game ends when the entire fleet has been destroyed.

For this package, I wanted to recreate this idea by having a randomly generated ship be hidden onto a board of nearly any size. Then the person playing the game can guess where the ship is.

## How to use the package

```{r setup, eval = FALSE}
library(battleship)

play(5,5) #creates a 5x5 board to find the ship
```
